### 2020-03-04 main_text/main_text.tex
Add expt details

@@

>>>>

	\subsection*{Materials and Methods}
	\paragraph*{Bacterial Strains.} Strains used in this work
	derive from {\it E. coli} K12 MG1655 with the {\it lac} operon
	removed and were constructed similarly to those used in
	\cite{RazoMejia 2018, Belliveau2019}. $\Delta{xapAB}$ and
	$\Delta{xapABR}$ knockouts were generated using the approach of
	Datsenko and Wanner \cite{Datsenko2000}. For the fluorescent
	reporter constructs the {\it xapAB} promoter region, with one or
	both XapR binding sites, were extracted from {\it E. coli} K12
	MG1655 by PCR. These were cloned into the YFP-expressing reporter
	plasmid pZS25,  containing kanamycin resistance, and integrated at
	the {\it galK} locus using $\lambda$ Red recombineering \cite{Sharan2009}.

	\paragraph*{Flow Cytometry Measurements.}
	Experimental measurements in Fig. 2B of the main text were obtained
	via flow cytometry and were performed in a similar manner as
	described in~\cite{RazoMejia2018}. Briefly, wild-type,
	$\Delta{xapABR}$, and $\Delta{xapAB}$ were grown to saturation in
	rich LB Miller (BD Medical) medium and were diluted 1:1000 into M9
	minimal medium supplemented with 0.5\% (w/v) glucose and the
	appropriate concentration of xanthosine. For measurements of the
	$\Delta{xapAB}$ strain, chloramphenicol was also added to the growth
	medium to ensure stability of the pZ3PN25-tetR plasmid along with 10
	ng /mL of anhydro-tetracycline to maximize expression of
	xapR-mCherry. Cultures were allowed to grow at 37$^\circ$ C for six
	to eight hours to an OD$_{600nm}$ of $\approx$ 0.3 At this point,
	the cultures were diluted 1:10 into M9 + 0.5\% glucose and were
	immediately analyzed via a MacsQuant VYB Flow Cytometery
	(MiltenyiBiotec). Measurement files were exported to CSV file
	formats and analyzed as previously described
	in~\cite{RazoMejia2018}.

@@

		\bibitem{Belliveau2019}
		Belliveau, NM, Barnes, SL, Ireland, WT,
		Jones, DL, Sweredoski, MJ, Moradian, A, et al.
		\newblock Systematic approach for dissecting the molecular
		mechanisms of transcriptional regulation in bacteria.
		\newblock PNAS, 2018;115(21), E4796–E4805.
		\newblock doi:{10.1073/pnas.1722055115}

		\bibitem{Datsenko2000}
		Datsenko, KA, Wanner, BL.
		\newblock One-step inactivation of chromosomal genes
		in Escherichia coli K-12 using PCR products.
		\newblock PNAS, 2000;97(12), 6640–6645.
		\newblock doi:{10.1073/pnas.120163297}

		\bibitem{Sharan2009}
		Sharan, SK, Thomason, LC, Kuznetsov, SG, Court, DL.
		\newblock Recombineering: a homologous recombination-based
		method of genetic engineering.
		\newblock Nature Protocols, 2009;4(2), 206–223.
		\newblock doi{10.1038/nprot.2008.227}
